Systematic Design of Optimal Low-Thrust Transfers for the Three-Body Problem \thanks{This research has been supported in part by NSF under the grants CMMI-1243000 (transferred from 1029551), CMMI-1335008, and CNS-1337722.}

### 2017-07-21 manuscript.tex
Update discussion of geo transfer

With each reachable set we move the controlled trajectory closer to the target stable manifold.
\Cref{fig:stage1to4_reachability,fig:stage5to8_reachability} shows all of the intermediate reachabiilty iterations to transfer between the initial orbit and the stable invariant manifold.
The complete transfer trajectory, after eight iterations, is shown in~\Cref{fig:geo_transfer}. 
Combining these trajectories results in the powered portion of the transfer from the geostationary orbit to the stable manifold. 
Each iteration systematically moves the reachable set towards the stable manifold. 
Furthermore, the optimal control formulation is simplified as each iteration is initialized using a simple distance metric on the \Poincare section.
\Cref{fig:geo_transfer_full,fig:geo_transfer_zoom} shows the resulting trajectory, with the final trajectory shown in red which ensures the intersection with the stable invariant manifold.
\Cref{fig:geo_transfer_poincare} shows the \Poincare section with the minimum reachable state from each iteration.
Each iteration seeks to decrease the distance to the stable manifold on the \Poincare section.
Furthermore, these minimum states serve to initialize each subsequent stage of the transfer. 
In this manner, there is a systematic and simple methodology to determine transfer trajectories.
Once at the stable manifold, no further control input is required and the vehicle will coast towards the target periodic orbit.
\Cref{fig:control_input_geo} shows the control input during the powered portion of the transfer. 
We utilize the same spacecraft assumption of \SI{500}{\kilo\gram} from~\cref{sec:periodic_orbit_transfer} which gives a maximum thrust of approximately \SI{1}{\newton}.
The spacecraft maintains a bounded control magnitude during the transfer to the stable manifold.
\begin{figure} 
        \centering 
        \subcaptionbox{Transfer trajectory: Complete trajectory consisting of eight iterations (1-7 black and final in red) of the reachability sets with a final control-free coast (blue)  on the stable manifold (green).\label{fig:geo_transfer_full}}{\includegraphics[width=0.45\textwidth]{geo_transfer_full}}\hfill
        \subcaptionbox{Detailed view of transfer: Centered at \(m_1\) the eight
            iterations from the reachability analysis are shown in black.  The
            final segment to the stable manifold is shown in red.  Each
            iteration progressively approaches the stable manifold.  Once on
        the stable manifold the vehicle can coast without thrust towards the
    periodic orbit.\label{fig:geo_transfer_zoom}
}{\includegraphics[width=0.45\textwidth]{geo_transfer_zoom}}

@@

This approach demonstrates the ability to link several computations of the reachability set to enable a more general transfer.
We use eight iterations in order to transfer from the geostationary orbit to the stable manifold.
This approach allows for a larger class of potential transfers which leverage the capabilities of low-thrust propulsion systems.
We are able to achieve a transfer that is not possible via the standard invariant manifold approach. 
In addition, this example illustrates a straightforward method to depart from the natural dynamics and transfer to a large region of the phase space that is not accessible via invariant manifolds alone.

>>>>

With each reachable set we move the controlled trajectory closer to the target stable manifold.
\Cref{fig:stage1to4_reachability,fig:stage5to8_reachability} shows all of the intermediate reachabiilty iterations to transfer between the initial orbit and the stable invariant manifold.
The complete transfer trajectory, after eight iterations, is shown in~\Cref{fig:geo_transfer}. 
Combining these trajectories results in the powered portion of the transfer from the geostationary orbit to the stable manifold. 
Each iteration systematically moves the reachable set towards the stable manifold. 
Furthermore, the optimal control formulation is simplified as each iteration is initialized using a simple distance metric on the \Poincare section.
\Cref{fig:geo_transfer_full,fig:geo_transfer_zoom} shows the resulting trajectory, with the final trajectory shown in red which ensures the intersection with the stable invariant manifold.
\Cref{fig:geo_transfer_poincare} shows the \Poincare section with the minimum reachable state from each iteration.
Each iteration seeks to decrease the distance to the stable manifold on the \Poincare section.
Furthermore, these minimum states serve to initialize each subsequent stage of the transfer. 
This method provides a systematic and simple methodology to determine transfer trajectories.
Instead of relying purely on numerical optimization to find an appropriate trajectory, our method instead utilizes the reachability set to determine suitable trajectories.
Once at the stable manifold, no further control input is required and the vehicle will coast towards the target periodic orbit.
\Cref{fig:control_input_geo} shows the control input during the powered portion of the transfer. 
We utilize the same spacecraft assumption of \SI{500}{\kilo\gram} from~\cref{sec:periodic_orbit_transfer} which gives a maximum thrust of approximately \SI{1}{\newton}.
The spacecraft maintains a bounded control magnitude during the transfer to the stable manifold.
\begin{figure} 
        \centering 
        \subcaptionbox{Transfer trajectory: Complete trajectory consisting of eight iterations (1-7 black and final in red) of the reachability sets with a final control-free coast (blue)  on the stable manifold (green).\label{fig:geo_transfer_full}}{\includegraphics[width=0.45\textwidth]{geo_transfer_full}}\hfill
        \subcaptionbox{Detailed view of transfer: Centered at \(m_1\) the eight
            iterations from the reachability analysis are shown in black.  The
            final segment to the stable manifold is shown in red.  Each
            iteration progressively approaches the stable manifold.  Once on
        the stable manifold the vehicle can coast without thrust towards the
    periodic orbit.\label{fig:geo_transfer_zoom}
}{\includegraphics[width=0.45\textwidth]{geo_transfer_zoom}}

@@

This numerical example demonstrates the ability to link several computations of the reachability set to enable a more general transfer.
We use eight iterations of computing the reachability set in order to transfer from the geostationary orbit to the stable manifold.
This approach allows for a larger class of potential transfers which leverage the capabilities of low-thrust propulsion systems.
We are able to achieve a transfer that is not possible via the standard invariant manifold approach. 
In addition, this example illustrates a straightforward method to depart from the natural dynamics and transfer to a large region of the phase space that is not accessible via invariant manifolds alone.
